\myTitle

### 2024-01-11 body-text-of-paper.tex
Another big slug of additions.

@@

\subsection*{An introductory motivating example}

Before we proceed to a description of the methodology used by \gscramble{},
we demonstrate a case in which using a standard sampling-with-replacement
approach induces RISPI when estimating admixture fractions.
To construct this simple example, we used the R programming language \citep{Rcoreteam} to
simulate allele frequencies for $L$ biallelic
loci in a single population from a $\mathrm{Beta}(1, 8)$ distribution and then simulated
two samples, $A$ and $B$, each of size $N$ diploid genotypes. The genotypes in $A$ and $B$ were simulated
from the same allele frequencies assuming Hardy-Weinberg equilibrium.

@@

\subsection*{Physical Linkage Matters}

ECA STILL NEEDS TO DESCRIBE AND INCLUDE THE SIMULATIONS THAT HE DID ON THIS.
THAT WORK IS ALL DONE, I JUST NEED TO PUT IT IN HERE, ALONG WITH THE FIGURE.

@@

Figure~\ref{fig:gsp1} shows an example GSP for the simple case
of simulating $F_2$ individuals. The figure and its caption
should be studied, as the following section
uses terminology that is defined in the figure caption.
%%%%%%%%%%%
\begin{figure}
\newcommand{\gspcapone}{\footnotesize
A genomic simulation pedigree (GSP) for simulating $F_2$ individuals.
Squares denote founder and non-founder nodes in the pedigree. There are four founders in the pedigree,
individuals 1--4.  The  triangles above each of those founders denotes, in color
and text, the population of origin of each of the two genomes within each founder.
Thus, individuals~1 and~2 are founders purely from population~$A$, and~3 and~4
are purely from population~$B$.  The pink hexagon labeled s7 is the sample node.
It represents samples that are taken from non-founder node~7, which, from the structure
of the pedigree, clearly represents an $F_2$ hybrid between populations $A$ and $B$.  The red numbers
on edges above and leading into each non-founder node indicate the number of
gametes that get segregated from the parent node (at the top of the edge) to the
daughter node (at the bottom of the edge).
This emphasizes that,
in dropping genes through a GSP, in contrast
to a traditional pedigree, each parent
node may segregate multiple gametes to a daughter node.  See the text for
further explanation.
Each non-founder node $x$ will have exactly two edges coming into it from above
(from its two parents), and we denote the numbers associated with those edges as $G^+_{x,1}$ and $G^+_{x,2}$.
For example, node 6 has $G^+_{6,1}=G^+_{6,2} = 2$.
A founder individual may have, at most, 2 edges coming downward out of it, while a non-founder individual may have more or less than two edges coming downward
out of it.  Letting $e_x$ be the number of downward edges out of node $x$ to its $e_x$
non-founder daughter nodes, we denote the number of gametes segregated
through each edge as $G^{-}_{x, 1},\ldots,G^{-}_{x, e_x}$.  For example, at
non-founder node~5, $e_5 = 1$ and $G^{-}_{5,1}=4$.
Finally, the purple number adjacent to the edge leading into the
sample node indicates how many sample individuals are drawn from individual
node 7. Any non-founder individual node can have a maximum of one edge leading
to a sample node.  We denote the number of samples emanating from node $x$ as $S_x$. In our example $S_7=4$ indicates that four $F_2$ individuals are
created from a single simulation on this GSP.
}
\begin{center}
\includegraphics[width=\columnwidth]{figures/F2.pdf}
\end{center}
\caption[\gspcapone]{\gspcapone}
\label{fig:gsp1}
\end{figure}
%%%%%%%%%%%%
It is important to understand that, apart from the founder nodes, the individual
nodes in a GSP do not necessarily represent only a single individual.  Specifically,
since we are preserving all genetic material, multiple gametes may get segregated
through each non-founder node in a GSP\@.

@@

In the \gscramble{} package there is a convenience function called {\footnotesize\tt create\_GSP()} that
will create GSPs for samples up to and including second-generation backcrosses (an example appears in Figure~\ref{fig:gsp2});
%%%%%
\begin{figure}
\newcommand{\gspcaptwo}{\footnotesize
An example GSP generated by {\footnotesize\tt create\_GSP()} that produces four different
admixture categories: one~$F_1$ in sample node~s7; two~$F_2$'s in sample node~s11; one $BC_1$ in sample node~s9; and two $BC_2$'s in sample node~s10.
}
\begin{center}
\includegraphics[width=\columnwidth]{figures/AllThem.pdf}
\end{center}
\caption[\gspcaptwo]{\gspcaptwo}
\label{fig:gsp2}
\end{figure}
%%%%
however, \gscramble{} is designed
to handle user-specified GSPs of arbitrary complexity.  When creating a unique GSP,
the following requirements are necessary for the GSP to be valid
and the simulation to execute successfully.
Writing $\founders$ for the set of all founder nodes, $\nonfound$ for the set of all non-founder nodes, and $\nonfounds$ for all non-founder
nodes that are not parents of other non-founders, but are adjacent to a sample node, $\nonfounde$ for all
non-founder nodes that have non-founder node daughters, but no sample nodes, and $\nonfoundse$ for all
non-founder nodes that are parents of non-founder nodes and also adjacent to sample-nodes, the necessary conditions
for a valid GSP, in addition to having no inbreeding loops, are:
\begin{equation}
\begin{aligned}
\sum_{x \in \nonfounds \cup \nonfoundse} S_x &= |\founders| &  \\
\sum_{i=1}^{e_x} G^-_{x,i} &= 2 & \forall x \in \founders \\
G^+_{x,1} &= G^+_{x,2} & \forall x \in \nonfound \\
\sum_{i=1}^{e_x} G^-_{x,i} &= G^+_{x,1} +  G^+_{x,2} & \forall x \in \nonfounde  \\
 S_x/2 + \sum_{i=1}^{e_x} G^-_{x,i} &= G^+_{x,1} +  G^+_{x,2} & ~~~\forall x \in \nonfoundse.  \\
\end{aligned}
\end{equation}
Before simulating from a GSP, \gscramble{} checks to ensure the GSP
satisfies these validity conditions.  The simulation of genomic segments
from founders to samples in a GSP is performed by the \gscramble{} function
{\footnotesize\tt segregate()}, which requires as input a list of GSPs through which
to segregate genomic segments, and, for each such GSP, a table that maps the
population labels on each GSP (in the inverted triangles atop the founders) to the
different sampled groups of individuals.

@@

HEY! I SHOULD ALSO DO A SET OF SIMULATIONS IN WHICH THE 65 MARKERS ARE
SIMULATED AS IF THEY ARE INDEPENDENTLY SEGREGATING---I THINK THAT MEANS
ASSIGNING EACH TO ITS OWN CHROMOSOME.  BUT MAYBE WORRY ABOUT THAT
LATER.

@@

The 160 invasive wild pig samples represented 120 reference individuals from the core regions of
3 populations (40 individuals each informed by previous analyses)
and 40 individuals from the contact regions of these populations.
We used ADMIXTURE version 1.3.0 \citep{alexander2009fast} to characterize the genetic structure
of the 160 samples (for $K = {1...6}$). Using the 120 reference individuals identified to represent population cores,
we sought to classify the admixture patterns of the 40 empirical samples
from the contact regions using simulated pedigrees from \gscramble{}. To address this objective we simulated
pedigrees to represent the likely classes of admixed individuals that would be present in the samples
from the contact regions of the 3 reference populations. The types of admixed individuals we considered were
$F_1$, $F_2$, $F_{1}BC_1$ and $F_{1}BC_2$ representing all two-population combinations
(Pop1 x Pop2, Pop1 x Pop3, Pop2 x Pop3, and reciprocally Pop2 x Pop1, Pop3 x Pop1, Pop3 x Pop2 as required
to simulate backcrossed classes).
We also simulated individuals from each of the founder populations. The first step of this workflow involved
simulating admixed individuals for 2 founder populations using one of the preset \gscramble{}
GSPs provided by the function {\footnotesize\tt create\_GSP()} for producing each of the types of admixed
individuals. Although we could have simulated all 4 types of admixed individuals from a single GSP (Figure~\ref{fig:gsp2}),
different numbers of simulated individuals are produced for each hybrid class. Therefore, for the sake of the
computational efficiency from simulating the exact number of desired individuals, we chose to simulate from
a single GSP for each of the hybrid classes by setting the corresponding hybrid parameter in {\footnotesize\tt create\_GSP()} to {\footnotesize\tt TRUE}. We used the default settings of the {\footnotesize\tt plink\_map2rec\_rates()} to specify the recombination rates. The 120 simulated genotypes were written to PLINK .ped and .map files using {\footnotesize\tt gscramble2plink()}. We used PLINK version 1.9 \citep{purcell2007plink} to convert the genotypes to binary files and used these as input into ADMIXTURE for which we specified $K=3$ to produce ancestry values. We iteratively
performed this workflow to produce 1,000 simulated genotypes and ancestry values for each of the
4 hybrid classes, as well as founder individuals, for each of the population combinations, for a total of
21,000 simulated individuals.

@@

\subsection*{An introductory motivating example}

@@

@@

PRETTY MUCH DONE HERE EXCEPT I WANT TO SIMULATE THINGS
UNLINKED.
%%%%%%%%%%
\begin{figure}
\newcommand{\nhbpcap}{\footnotesize Gonna need a caption}
\includegraphics[width=\columnwidth]{figures/newhybs-texed-crop.pdf}
\caption[\nhbpcap]{\nhbpcap}
\label{fig:newhyb-sims-barplot}
\end{figure}
%%%%%%%%%%

@@

The simulated hybrid classes produce
the expected range of admixture with $F_1$ and $F_2$ individuals having mean $Q=0.5$, with $F_2$ individuals having
more variation (Figure~\ref{fig:pig-sim-qs}A).
Backcrossed individuals have higher ancestry associated with the backcrossed population with mean $Q$
approximately $0.75$ ($BC_1$) and $0.87$ ($BC_2$) (Figure~\ref{fig:pig-sim-qs}A). Notably, the simulated
$F_1$ hybrids have the most variation in the distribution of the $Q$ values associated with each of the genetic clusters.
When the estimated Q values for the $F_1$ hybrids are separated by the population combinations,
$F_1$ hybrids for Pop1-Pop2 have the least variation around $q=0.5$ (standard deviation
= 0.008), while Pop1-Pop3 and Pop2-Pop3
have higher variation (standard deviation = 0.011-0.016) (Figure~\ref{fig:pig-sim-qs}B). Also, all $Q$
distributions for $F_1$ hybrids, regardless of population combination, center around
$0.50$ except for the two distributions
of Pop3, which have a mean of $Q=0.49$ (Figure~\ref{fig:pig-sim-qs}B).
The differences among these
distributions of $Q$ values for the simulated data reflect the genetic differences observed
in the empirical data, specifically, that genetic differentiation is highest between Pop1 and Pop2 and that
Pop14 is the most admixed population with ancestry contributions from both Pop1 and Pop2.

%%%
\begin{figure*}
\newcommand{\pigsimsqscap}{\footnotesize (A) The density of the estimated Q values from ADMIXTURE for
the simulated runs are
grouped across all population-combinations for each hybrid class and colored by the $K$ genetic cluster
(e.g., the Pop1 density plot for the $F_{1}BC_1$ plots the Pop1 genetic cluster for both
the Pop1-Pop2 and Pop1-Pop3 combinations). The density plots across the $K$
genetic clusters are mostly similar with the most variation among the genetic clusters evident in
the $F_1$ plot. (B) Plotting the density of the estimated Q values from ADMIXTURE for the $F_1$ hybrids,
separated by the population combinations, reveals the least variance in estimated Q values for
Pop1-Pop2 compared to Pop1-Pop3 and Pop2-Pop3. Note that these population combinations group the
reciprocal population combination in each plot (e.g., "Pop1\_Pop2" has simulations
from both Pop1-Pop2 and Pop2-Pop1).}
\includegraphics[width=0.96\textwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure*}
%%%

>>>>

%%%%%%%%%%%
\begin{figure}
\newcommand{\gspcapone}{\footnotesize
A genomic simulation pedigree (GSP) for simulating $F_2$ individuals.
Squares denote founder and non-founder nodes in the pedigree. There are four founders in the pedigree,
individuals 1--4.  The  triangles above each of those founders denotes, in color
and text, the population of origin of each of the two genomes within each founder.
Thus, individuals~1 and~2 are founders purely from population~$A$, and~3 and~4
are purely from population~$B$.  The pink hexagon labeled s7 is the sample node.
It represents samples that are taken from non-founder node~7, which, from the structure
of the pedigree, clearly represents an $F_2$ hybrid between populations $A$ and $B$.  The red numbers
on edges above and leading into each non-founder node indicate the number of
gametes that get segregated from the parent node (at the top of the edge) to the
daughter node (at the bottom of the edge).
This emphasizes that,
in dropping genes through a GSP, in contrast
to a traditional pedigree, each parent
node may segregate multiple gametes to a daughter node.  See the text for
further explanation.
Each non-founder node $x$ will have exactly two edges coming into it from above
(from its two parents), and we denote the numbers associated with those edges as $G^+_{x,1}$ and $G^+_{x,2}$.
For example, node 6 has $G^+_{6,1}=G^+_{6,2} = 2$.
A founder individual may have, at most, 2 edges coming downward out of it, while a non-founder individual may have more or less than two edges coming downward
out of it.  Letting $e_x$ be the number of downward edges out of node $x$ to its $e_x$
non-founder daughter nodes, we denote the number of gametes segregated
through each edge as $G^{-}_{x, 1},\ldots,G^{-}_{x, e_x}$.  For example, at
non-founder node~5, $e_5 = 1$ and $G^{-}_{5,1}=4$.
Finally, the purple number adjacent to the edge leading into the
sample node indicates how many sample individuals are drawn from individual
node 7. Any non-founder individual node can have a maximum of one edge leading
to a sample node.  We denote the number of samples emanating from node $x$ as $S_x$. In our example $S_7=4$ indicates that four $F_2$ individuals are
created from a single simulation on this GSP.
}
\begin{center}
\includegraphics[width=\columnwidth]{figures/F2.pdf}
\end{center}
\caption[\gspcapone]{\gspcapone}
\label{fig:gsp1}
\end{figure}
%%%%%%%%%%%%
%%%%%
\begin{figure}
\newcommand{\gspcaptwo}{\footnotesize
An example GSP generated by {\footnotesize\tt create\_GSP()} that produces four different
admixture categories: one~$F_1$ in sample node~s7; two~$F_2$'s in sample node~s11; one $\BC_1$ in sample node~s9; and two $\BC_2$'s in sample node~s10.
}
\begin{center}
\includegraphics[width=\columnwidth]{figures/AllThem.pdf}
\end{center}
\caption[\gspcaptwo]{\gspcaptwo}
\label{fig:gsp2}
\end{figure}
%%%%

@@

\subsection*{Two introductory motivating examples}

Before we proceed to a description of the methodology used by \gscramble{},
we demonstrate two important points through two simple simulations.  In the first,
we show that using a standard sampling-with-replacement
approach induces RISPI when estimating admixture fractions. In the second, we show
the effect of physical linkage on the distribution of admixture fractions of hybrid individuals,
which vividly shows why it is not acceptable with large numbers of markers, to simulate
the genotypes of hybrid individuals assuming no physical linkage.

\subsubsection*{RISPI when estimating admixture fractions}

To construct this simple example, we used the R programming language \citep{Rcoreteam} to
simulate allele frequencies for $L$ biallelic
loci in a single population from a $\mathrm{Beta}(1, 8)$ distribution and then simulated
two samples, $A$ and $B$, each of size $N$ diploid genotypes. The genotypes in $A$ and $B$ were simulated
from the same allele frequencies assuming Hardy-Weinberg equilibrium.

@@

\subsubsection*{Physical Linkage in Hybrid Individuals}

We first simulated the genotypes of hybrids between two species, $a$ and $b$,
considering $F_2$'s and first- through
fourth-generation backcrosses in each direction, erroneously treating each
locus as if it were independently segregating (as done, for example, in {\sc HybridLab}). Thus,
each locus independently is simulated to have a genotype of 2, 1, or 0 gene copies originating from species $a$ [{\em e.g.}~genotypes of $(a,a)$, $(a,b)$, or $(b,b)$] according to the expected
probability of each genotype given the hybrid category (see \citealt{anderson2002model}).
48,000 hybrids were simulated at each number of loci, $L$, in $\{10^2, 10^3, 10^4, 10^5\}$.
The admixture fraction of each simulated individual was recorded as the fraction of all $2L$
gene copies originating from species $a$.

We also simulated the genomes of 48,000 individuals of each
hybrid category using \gscramble{}'s {\footnotesize\tt segregate()} function, as described
below, with number of chromosomes and sex-averaged recombination rates
for pigs, as estimated by from \citet{tortereau2012high}. In this case, we recorded the
admixture fraction of each simulated individual as the fraction of all genome segments
that originated from species~$a$.  This provides the distribution of the true admixture fraction
when physical linkage of markers is not ignored.

All the admixture fraction distributions were summarized by plotting them as histograms
so they could be compared easily.

@@

Figure~\ref{fig:gsp1} shows an example GSP for the simple case
of simulating $F_2$ individuals. The figure and its caption
should be studied, as the following section
uses terminology that is defined in the figure caption.

It is important to understand that, apart from the founder nodes, the individual
nodes in a GSP do not necessarily represent only a single individual.  Specifically,
since we are preserving all genetic material, multiple gametes may get segregated
through each non-founder node in a GSP\@.

@@

In the \gscramble{} package there is a convenience function called {\footnotesize\tt create\_GSP()} that
will create GSPs for samples up to and including second-generation backcrosses (an example appears in Figure~\ref{fig:gsp2});
however, \gscramble{} is designed
to handle user-specified GSPs of arbitrary complexity.  When creating a unique GSP,
the following requirements are necessary for the GSP to be valid
and the simulation to execute successfully.
Writing $\founders$ for the set of all founder nodes, $\nonfound$ for the set of all non-founder nodes, and $\nonfounds$ for all non-founder
nodes that are not parents of other non-founders, but are adjacent to a sample node, $\nonfounde$ for all
non-founder nodes that have non-founder node daughters, but no sample nodes, and $\nonfoundse$ for all
non-founder nodes that are parents of non-founder nodes and also adjacent to sample-nodes, the necessary conditions
for a valid GSP, in addition to having no inbreeding loops, are:
\begin{equation}
\begin{aligned}
\sum_{x \in \nonfounds \cup \nonfoundse} S_x &= |\founders| &  \\
\sum_{i=1}^{e_x} G^-_{x,i} &= 2 & \forall x \in \founders \\
G^+_{x,1} &= G^+_{x,2} & \forall x \in \nonfound \\
\sum_{i=1}^{e_x} G^-_{x,i} &= G^+_{x,1} +  G^+_{x,2} & \forall x \in \nonfounde  \\
 S_x/2 + \sum_{i=1}^{e_x} G^-_{x,i} &= G^+_{x,1} +  G^+_{x,2} & ~~~\forall x \in \nonfoundse.  \\
\end{aligned}
\end{equation}
Before simulating from a GSP, \gscramble{} checks to ensure the GSP
satisfies these validity conditions.  The simulation of genomic segments
from founders to samples in a GSP is performed by the \gscramble{} function
{\footnotesize\tt segregate()}, which requires as input a list of GSPs through which
to segregate genomic segments, and, for each such GSP, a table that maps the
population labels on each GSP (in the inverted triangles atop the founders) to the
different sampled groups of individuals.

@@

@@

The 160 invasive wild pig samples represented 120 reference individuals from the core regions of
3 populations (40 individuals each informed by previous analyses)
and 40 individuals from the contact regions of these populations.
We used ADMIXTURE version 1.3.0 \citep{alexander2009fast} to characterize the genetic structure
of the 160 samples (for $K = {1...6}$). Using the 120 reference individuals identified to represent population cores,
we sought to classify the admixture patterns of the 40 empirical samples
from the contact regions using simulated pedigrees from \gscramble{}. To address this objective we simulated
pedigrees to represent the likely classes of admixed individuals that would be present in the samples
from the contact regions of the 3 reference populations. The types of admixed individuals we considered were
$F_1$, $F_2$, $F_{1}\BC_1$ and $F_{1}\BC_2$ representing all two-population combinations
(Pop1 x Pop2, Pop1 x Pop3, Pop2 x Pop3, and reciprocally Pop2 x Pop1, Pop3 x Pop1, Pop3 x Pop2 as required
to simulate backcrossed classes).
We also simulated individuals from each of the founder populations. The first step of this workflow involved
simulating admixed individuals for 2 founder populations using one of the preset \gscramble{}
GSPs provided by the function {\footnotesize\tt create\_GSP()} for producing each of the types of admixed
individuals. Although we could have simulated all 4 types of admixed individuals from a single GSP (Figure~\ref{fig:gsp2}),
different numbers of simulated individuals are produced for each hybrid class. Therefore, for the sake of the
computational efficiency from simulating the exact number of desired individuals, we chose to simulate from
a single GSP for each of the hybrid classes by setting the corresponding hybrid parameter in {\footnotesize\tt create\_GSP()} to {\footnotesize\tt TRUE}. We used the default settings of the {\footnotesize\tt plink\_map2rec\_rates()} to specify the recombination rates. The 120 simulated genotypes were written to PLINK .ped and .map files using {\footnotesize\tt gscramble2plink()}. We used PLINK version 1.9 \citep{purcell2007plink} to convert the genotypes to binary files and used these as input into ADMIXTURE for which we specified $K=3$ to produce ancestry values. We iteratively
performed this workflow to produce 1,000 simulated genotypes and ancestry values for each of the
4 hybrid classes, as well as founder individuals, for each of the population combinations, for a total of
21,000 simulated individuals.

@@

\subsection*{Two Introductory Motivating Examples}

\subsubsection*{RISPI when estimating admixture fractions}

@@

\subsubsection*{Physical Linkage in Hybrid Individuals}

Figure is completed and is in Fig.~\ref{fig:ad-fract-sims}.
%%%%%%%%%%
\begin{figure}
\newcommand{\adfcap}{\footnotesize Admixture fractions of individuals simulated
assuming no physical linkage (top four panels)
and when physical linkage is simulated using \gscramble{}.  In the top 4 panels the number
of simulated loci appears in the panel header.  Failing to simulate markers with physical linkage
produces distributions of admixture fractions that are far more narrow than reality, giving the
mistaken impression that admixture fractions of different hybrid categories do not overlap.  }
\includegraphics[width=\columnwidth]{figures/link-and-nolink-sims-crop.pdf}
\caption[\adfcap]{\adfcap}
\label{fig:ad-fract-sims}
\end{figure}
%%%%%%%%%%
\subsection*{Empirical Examples}

@@

Figure is completed and is Fig.~\ref{fig:newhyb-sims-barplot}
%%%%%%%%%%
\begin{figure}
\newcommand{\nhbpcap}{\footnotesize Posterior probabilities for simulated
individuals of different trout hybrid categories.  Each pair of plots shows the results
for individuals of the true hybrid category listed atop the pair.  (See Table~\protect\ref{tab:newhybcats} for meaning of the names.)  The top panel of each pair
shows results for fish simulated with the 30 markers used by \protect\citet{rizza2023limited}, and the bottom panel shows results for fish simulated an additional  35 markers, some of which are linked
on the same chromosome. Each individual appears as a thin vertical line, posterior probabilities of
each inferred hybrid category are indicated by extent of different colors on those lines.  Individuals
are sorted according to maximum {\em a posteriori} hybrid category, and, within that by the
maximum posterior probability. }
{\centering
\includegraphics[width=0.98\columnwidth]{figures/newhybs-texed-crop.pdf}
}
\caption[\nhbpcap]{\nhbpcap}
\label{fig:newhyb-sims-barplot}
\end{figure}
%%%%%%%%%%

@@

The simulated hybrid classes produce
the expected range of admixture with $F_1$ and $F_2$ individuals having mean $Q=0.5$, with $F_2$ individuals having
more variation (Figure~\ref{fig:pig-sim-qs}A).
Backcrossed individuals have higher ancestry associated with the backcrossed population with mean $Q$
approximately $0.75$ ($\BC_1$) and $0.87$ ($\BC_2$) (Figure~\ref{fig:pig-sim-qs}A). Notably, the simulated
$F_1$ hybrids have the most variation in the distribution of the $Q$ values associated with each of the genetic clusters.
When the estimated Q values for the $F_1$ hybrids are separated by the population combinations,
$F_1$ hybrids for Pop1-Pop2 have the least variation around $q=0.5$ (standard deviation
= 0.008), while Pop1-Pop3 and Pop2-Pop3
have higher variation (standard deviation = 0.011-0.016) (Figure~\ref{fig:pig-sim-qs}B). Also, all $Q$
distributions for $F_1$ hybrids, regardless of population combination, center around
$0.50$ except for the two distributions
of Pop3, which have a mean of $Q=0.49$ (Figure~\ref{fig:pig-sim-qs}B).
The differences among these
distributions of $Q$ values for the simulated data reflect the genetic differences observed
in the empirical data, specifically, that genetic differentiation is highest between Pop1 and Pop2 and that
Pop14 is the most admixed population with ancestry contributions from both Pop1 and Pop2.

%%%
\begin{figure}
\newcommand{\pigsimsqscap}{\footnotesize (A) The density of the estimated Q values from ADMIXTURE for
the simulated runs are
grouped across all population-combinations for each hybrid class and colored by the $K$ genetic cluster
(e.g., the Pop1 density plot for the $F_{1}\BC_1$ plots the Pop1 genetic cluster for both
the Pop1-Pop2 and Pop1-Pop3 combinations). The density plots across the $K$
genetic clusters are mostly similar with the most variation among the genetic clusters evident in
the $F_1$ plot. (B) Plotting the density of the estimated Q values from ADMIXTURE for the $F_1$ hybrids,
separated by the population combinations, reveals the least variance in estimated Q values for
Pop1-Pop2 compared to Pop1-Pop3 and Pop2-Pop3. Note that these population combinations group the
reciprocal population combination in each plot (e.g., "Pop1\_Pop2" has simulations
from both Pop1-Pop2 and Pop2-Pop1).}
\includegraphics[width=\columnwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure}
%%%
